Pre-registration

### 2020-06-10 docs/paper.Rmd

```{r message=FALSE, warning=FALSE, include=FALSE, echo=FALSE}
library(knitr)
#install.packages("KableExtra")
library(kableExtra)
library(dplyr)
#install.packages("captioner")
library(captioner)
#install.packages("estimatr")
library(estimatr)
library(texreg)

@@

```{r include=FALSE}
table_nums <- captioner(prefix = "Table")
fig_nums   <- captioner(prefix = "Figure")
```

```{r message=FALSE, warning=FALSE, include=FALSE}
anx_nums<-captioner(prefix = "Annexed")

@@

![`r fb`](../output/images/corpoly.png){ width=70% }
</center>

@@

tb.col  <- c("Variables",1:4,1:4,1:4)
tb.caption <- "Factor loadings and fit measures" 
tb.foot <- paste0("Standardised factor loadings using DWLS estimator")

@@

tb.fm01<- kable(tb.fm, format = table_format, booktabs = T,linesep = "", escape = FALSE,align = "lcccccccccccc",col.names = tb.col, caption = loadfit) %>% 
          kable_styling(full_width = table_format2,latex_options = c("hold_position","scale_down"), position = "center",font_size = 9) %>% 
          add_header_above(header = c(" "=1,"Version 1"= 4,"Version 2"= 4,"Version 3"= 4)) %>% 
          add_header_above(header = c(" "=1,"Factor loadings"= 12)) %>% 
          row_spec(row = 8,hline_after = TRUE) %>%
          add_indent(c(9:12))  %>%
          footnote(general = tb.foot, number = c("CFI = Comparative fit index (scaled); ", " RMSEA = Root mean square error of approximation (scaled); "));tb.fm01

>>>>

```{r message=FALSE, warning=FALSE, include=FALSE, echo=FALSE}
library(knitr)
#install.packages("KableExtra")
library(kableExtra)
library(dplyr)
#install.packages("captioner")
library(captioner)
#install.packages("estimatr")
```

@@

```{r include=FALSE}
table_nums <- captioner(prefix = "Table")
fig_nums   <- captioner(prefix = "Figure")
anx_nums<-captioner(prefix = "Annexed")
```

@@

![`r fb`](../output/images/corpoly.png){ width=70% }

@@

tb.col  <- c("Variables",1:4,1:4,1:4)
tb.caption <- "Factor loadings and fit measures" 
tb.foot <- paste0("Standardised factor loadings using DWLS estimator ; CFI = Comparative fit index (scaled); RMSEA = Root mean square error of approximation (scaled)")

@@

tb.fm01<- kable(tb.fm, format = table_format, booktabs = T,linesep = "", escape = FALSE,align = "lcccccccccccc",col.names = tb.col, caption = loadfit) %>% 
          kable_styling(full_width = table_format2,latex_options = c("hold_position","scale_down"), position = "center",font_size = 9) %>% 
          add_header_above(header = c(" "=1,"Version 1"= 4,"Version 2"= 4,"Version 3"= 4)) %>% 
          add_header_above(header = c(" "=1,"Factor loadings"= 12)) %>% 
          row_spec(row = 8,hline_after = TRUE) %>%
          add_indent(c(9:12))  %>%
          footnote(general = tb.foot,threeparttable = T);tb.fm01

### 2020-06-10 input/preanalysis/preanalisis.Rmd

# tab01 <- read.csv(file = "input/data/original/materials/table01.csv",header = 1,sep = ";")
#
# cnames <- c("Dimension", "Factor","Statement (english)" , "Statement (spanish)")
#
# caption01 <- capTab("Meritocracy perception and preference")
# kable(tab01,format = table_format,booktabs = T, linesep = "",col.names = cnames, caption = caption01) %>%
#   kable_styling(full_width = T,latex_options = c("hold_position","scale_down"),position = "center",font_size = 9) %>%
#   column_spec(column = 1,width = "1.5cm",) %>%
#   column_spec(column = 2,width = "2 cm") %>%
#   collapse_rows(columns = 1:2,valign = "middle")

>>>>

 #tab01 <- read.csv(file = "input/data/original/materials/table01.csv",header = 1,sep = ";")

 cnames <- c("Dimension", "Factor","Statement (english)" , "Statement (spanish)")

 caption01 <- capTab("Meritocracy perception and preference")
 kable(tab01,format = table_format,booktabs = T, linesep = "",col.names = cnames, caption = caption01) %>%
   kable_styling(full_width = T,latex_options = c("hold_position","scale_down"),position = "center",font_size = 9) %>%
   column_spec(column = 1,width = "1.5cm",) %>%
   column_spec(column = 2,width = "2 cm") %>%
   collapse_rows(columns = 1:2,valign = "middle")
